\thetitle

### 2013-04-13 tfpie/tfpie.tex
Outline.

\paragraph{Outline} The remainder of this paper is organized as follows\dots

>>>>

\paragraph{Outline} The remainder of this paper is organized as follows:
in section~\ref{sec:background} provides background on \emph{How to
  Design Programs} and the context and constraints involved in the
first-year at Northeastern.  Section~\ref{sec:shift} describes our
approach to the second semester, which starts with a small shift in
perspective to bridge the gap between functional programming and
object oriented programming.  Section~\ref{sec:industrial} describes
the path toward programming in an industrial object-oriented
programming language.  Section~\ref{sec:related-work} discusses the
relation to existing work and section~\ref{sec:conclusion} concludes.
